---
title: "chapter04_lm_4assums"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

1. linearity

```{r}
par(mfrow=c(1,2))
x = c(1,2,4,8,16)
y = c(1,2,3,4,5)
plot(x, y, type='b', lwd=3, main='Before Transformation')
x_adj = log(x)
plot(x_adj, y, type='b', lwd=3, main='After Transformation')
```

2. homogeneity

```{r}
library(Lahman)
rec = subset(Teams, yearID == 2014)
rec$wp = rec$W / rec$G
a = lm(wp~R, rec)
library(lmtest)
bptest(a)
```

It implies strong heteroscedasticity
=> Do Box Cox Transformation!
=> We can get a little improvement

```{r }
library(caret)
b = BoxCoxTrans(rec$wp)
c = cbind(rec, wp_adj=predict(b, rec$wp))
d = lm(wp_adj~R, c)
bptest(d)
```


3. independence
  1) Errors of dependent variables not correlated with errors of independent variables.
  2) Errors of dependent variables are independent each other dependent variables.


4. normality

ERA and avg models for estimating winning rate


```{r}
library(Lahman)
rec = subset(Teams, yearID == 2014)
rec$wp = rec$W/rec$G
rec$avg = rec$H / rec$AB
avg_model = lm(wp~avg, rec)
ERA_model = lm(wp~ERA, rec)
```


### About Residual Standard Error

If we use small residual standard error, we can narrow confidence and prediction interval so that we can improve the decisions.
Otherwise, it's not helpful for decision making.

avg_model

```{r}
summary(avg_model)
```

ERA model :

```{r}
summary(ERA_model)
```




