---
title: "chapter04_inference"
output:
  pdf_document :
    latex_engine : xelatex
  html_document : default
mainfont : NanumGothic
---


```{r}
library(Lahman)
a = subset(Teams, yearID>2000)
attach(a)
a$avg = H/AB
a$wp = W/G
lm(wp~avg, a)
```

pwr.f2.test gives a minimum samples for linear regression

```{r}
library(pwr)
pwr.f2.test(1, NULL, 0.01, 0.05, 0.95)
```

Do linear regression

```{r}
a = subset(Teams, lgID == 'AL' | lgID=='NL')
b = sample(1:nrow(a), 1302)
c = a[b,]
c$avg = c$H / c$AB
c$wp = c$W/c$G
d = lm(wp~avg, data=c)
summary(d)
```

F-statistics can be derived that between grouup deviation divided by within-group deviation
Inspection of the effectivess of new variable
If it is useless and no impact to explain our model, we can not reject the Hypothesis.

H0 : existing model = new model
existing model => Winning ratio = beta_0 + error
new model => winning ratio = beta_0 + beta_1*batting_avg + error

```{r}
summary.aov(d)
```

so, we can reject the H0 and we can inspect new model is more effective than existing one.



confidence interval and predicted interval
```{r}
e = data.frame(avg = 0.270)
predict(d, e, level=0.95, interval = 'confidence')
```

```{r}
e = data.frame(avg = 0.270)
predict(d, e, level=0.95, interval = 'predict')
```

